 
---
title: Your title here!

author: |
  | Author 1^[Corresponding author: email@email.com] $^1$, Author 2 $^1$, Author 3 $^2$
  | $^1$Affiliation1,  $^2$Affiliation2

abstract: |
  Your abstract goes here...

bibliography: Path to your .bib file
csl: Path to your .csl file #sets the style of your bibliography

output:
  bookdown::pdf_document2:
  toc: no
fig_caption: yes

always_allow_html: yes

# These are LaTex settings to take care of floating figures/tables, line spacing, etc
header-includes:
  - \usepackage{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
---

[Hemendik[(landscapeportal.org/blog/2017/09/06/r-markdown-template-for-a-scientific-manuscript/) hartutako eredua; Geoscience Lab-eko blogeko Basic R markdown template for writing a scientific manuscript.

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=300)

# I usually load my libraries up front to keep things organized
library(bookdown)
library(knitr)
library(kableExtra)
library(ggplot2)
library(ggthemes)
library(ggExtra)
library(dplyr)
library(stringr)

```

From here it's normal R markdown, but with a bookdown flavour. Here are some pointers:

+ Headers are specified with #, ##, ###, etc. for H1, H2, H3, etc.
+ When you would like to cite a paper, your citation looks like this: [@Key] - e.g. [@author2017]
+ If you would like to add a figure, this can be done with an R snippet:


```{r figRef, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Figure caption here"}
## R code here, with plot output at end, for example using ggplot2

```

+ To cross-reference figures in your text, simply write something like: As shown in Figure  \@ref(fig:figRef) ...
+ Tables can be added using the kable function from knitr, for example:

```{r tabRef, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}

df <- read.csv(...)

knitr::kable(df, caption = "Table caption here...", booktabs = TRUE)
```


# Erreferentziak
